### 2019-11-13 report/02-methods.Rmd
Update report

net_list %<>%
  left_join(dplyr::select(size_analysis, date, biomass))
#Node position:
node <- net_list$network %>% unlist(., use.names = FALSE) %>% unique
test <- graph_from_adjacency_matrix(meta$metaweb) %>% as_data_frame %>%
  mutate_all(list(~str_extract_all(., "[a-zA-Z]+", simplify = TRUE))) %>%
  distinct(from, to)
node_position <- create_layout(graph_from_data_frame(test), layout = "kk")$x
names(node_position) <- create_layout(graph_from_data_frame(test), layout = "kk")$name
#color:
color <- set_color_species(node_list = node, species_list = NULL,
  resource_list = NULL,
  col_resource = NULL)

@@

@@

>>>>

net_list %<>%
  left_join(dplyr::select(size_analysis, date, biomass))
#Node position:
node <- net_list$network %>% unlist(., use.names = FALSE) %>% unique
test <- graph_from_adjacency_matrix(meta$metaweb) %>%
  igraph::as_data_frame(.) %>%
  mutate_all(list(~str_extract_all(., "[a-zA-Z]+", simplify = TRUE))) %>%
  distinct(from, to)
node_position <- create_layout(graph_from_data_frame(test), layout = "kk")$x
names(node_position) <- create_layout(graph_from_data_frame(test), layout = "kk")$name
#color:
color <- set_color_species(node_list = node, species_list = NULL,
  resource_list = NULL,
  col_resource = NULL)

@@

```{r}
myload(temporal_station_desc, temporal_press_polluants, dir = data_common)
myload(hab_analysis, geo_station, dir = data_common)

habitat <- hab_analysis %>%
  mutate_all(list(as.factor)) %>%
  select(-opcod, -station, -aqua_vg)

lvl <- c("null", "weak", "medium", "high")
lvl_sinuosite <- c("straight", "sinuous", "very_sinuous", "meandering")
lvl_shade <- c("clear", "quite_clear", "quite_covered", "covered")

habitat_station <- hab_analysis %>%
  select(-opcod, -aqua_vg, - shade, - sinuosite) %>%
  mutate_if(is.character, list(~factor(., levels = lvl, ordered = TRUE))) %>%
  left_join(select(hab_analysis, station, shade, sinuosite)) %>%
  mutate(
    shade = factor(shade, levels = lvl_shade, ordered = TRUE),
    sinuosite = factor(sinuosite, levels = lvl_sinuosite, ordered = TRUE)) %>%
  group_by(station) %>%
  summarise_all(list(med = ~median(as.numeric(.), na.rm = TRUE))) %>%
  left_join(select(temporal_station_desc, station, width_river_mean, avg_depth_station_mean))

# Add alt, lat, etc...
habitat_station %<>% 
  left_join(geo_station, by = "station") %>%
  select(-region_csp)
# Add temp and flow
flow_temp <- temporal_press_polluants %>%
  filter(category %in% c("flow", "temperature", "DBO", "herbicides",
      "fungicides", "insecticides", "nitrates", "phosphore")) %>%
  rename(station = id) %>%
  select(station, category, press_med) %>%
  spread(category, press_med)

habitat_station %<>%
  left_join(flow_temp, by = "station")
```

```{r pca-hab, fig.dim = c(10, 7), fig.cap = "PCA over habitat description"}
library(ade4)
library(factoextra)
pca_hab <- dudi.pca(as.data.frame(select(na.omit(habitat_station), -station)), scannf = FALSE, nf = 2, center = TRUE, scale = TRUE)

eig_plot <- fviz_eig(pca_hab)
pca_plot <- fviz_pca_var(pca_hab,
    axes = c(1, 2),
    col.var = "contrib", # Color by contributions to the PC
    gradient.cols = c("#00AFBB", "#E7B800", "#FC4E07"),
    repel = TRUE     # Avoid text overlapping
  )

ggdraw(pca_plot) + 
  draw_plot(eig_plot, x = .7, y = .95, hjust = 1, vjust = 1, width = 0.17, height = 0.25)
```

The PCA (Fig. \@ref(fig:pca-hab)) showed unsurprisingly that order of strahler, the
depth, width of the river and distance to source and avg flow are closely
linked. Altitude, slope and the amount of rocky shelter are also closely linked.
Station of larger latitude had also higher DBO and phosphorus, higher annual
mean temperature and more vegetation.  The first axis of the PCA (ordinate)
discriminated station located far from the source (which are large, deep, with a
big annual flow and high strahler order) from the shady station, which are
sinuous, with a variety of habitat such as under bank and logjam.
The second axis (abscissa) discriminated station in altitude with high slope,
composed of rocky habitat from the ones that had higher average annual
temperature located in the south, with more enrichment (DBO, nitrates,
phosphorus) and that are more vegetated.

@@

#### Press category

```{r press-units, fig.cap = "All the parameters collected together with their units"}
# Put units to present all the parameters
myload(polluant_units, dir = mypath("data-raw", "polluants", "naiades_data"))
kable(polluant_units) %>%
  kable_styling() %>%
  scroll_box(width = "100%", height = "400px")
```

```{r press-cat, fig.cap = "Molecules of pressure by category together with their toxicity if relevant or available"}
myload(press_cat, dir = mypath("data-raw", "polluants"))
kable(arrange(press_cat, category)) %>%
  kable_styling() %>%
  scroll_box(width = "100%", height = "400px")
```

#### Press trough time

```{r press-time, fig.cap = "Average press category over the station through time. The pesticides are expressed in Toxic Unit (TU)."}
myload(press_metrics, dir = mypath("data"))
ggplot(press_metrics, aes(y = press, x = year)) +
  stat_summary(fun.y = "mean", geom = "line") +
  stat_summary(geom="ribbon", fun.data=mean_cl_normal, colour=NA,alpha=0.1)+
  facet_wrap(~category, scales = "free_y")
```

Most of the pressure decreased through time expect notably the nitrates and the
temperature (Fig. \@ref(fig:press-time)). **Be careful, there are certainly a
biais in temperature increase because the number of station that have been
sampled. It would be nice to look at the tendency by station.**

### 2019-11-13 report/03-results.Rmd
Update report

```{r net-cor-med, fig.cap = "Correlation between network indices (median over the temporal series). "}
# Get network metrics
myload(temporal_network_metrics, dir = dest_dir)
myload(temporal_community_metrics, synchrony, dir = data_common)

@@

temp_plot <- plot_grid(plotlist = pca_plot)
plot_grid(temp_plot, eig_plot)
```

@@

## Productivity

## Stability of biomass

### Some temporal series of biomass

```{r}
myload(community_metrics, dir = data_common)
community_metrics %<>% left_join(select(op_analysis, opcod, station, date))
station_high_low_stab <- temporal_community_metrics %>%
  arrange(desc(biomass_stab)) %>%
  slice(c(1:5, (n() - 4):(n() - 0))) %>%
  select(station) %>%
  unlist
names(station_high_low_stab) <- rep(c("high", "low"), each = 5) 
```

```{r tmp-stab, fig.dim = c(10, 7), fig.cap = "The five lowest and highest biomass stability"}
temporal_biomass <- community_metrics %>%
  filter(station %in% station_high_low_stab) %>%
  mutate(stab_status = ifelse(
      station %in% station_high_low_stab[names(station_high_low_stab) == "low"],
      "low", "high")) %>%
  group_by(stab_status, station) %>%
  nest() %>%
  group_by(stab_status) %>%
  mutate(id_stab = seq_along(station)) %>%
  unnest()
ggplot(temporal_biomass, aes(y = biomass, x = date)) +
  geom_line() +
  geom_point() +
  facet_grid(id_stab ~ stab_status, scales = "free_y") +
  labs(y = "Biomass (g)", x = "Date")
```

### Map stability

```{r}
myload(station_analysis, region_polygon, dir = data_common)
stab <- temporal_community_metrics %>% 
  select(station, biomass_stab)
station_stab <- left_join(station_analysis, rename(stab, id = station)) %>%
  filter(!is.na(biomass_stab))
ggplot(data = region_polygon) +
    geom_sf() +
    geom_sf(data = station_stab, aes(color = log(biomass_stab)), size = 4) +
    scale_color_gradient(low = "red", high = "green")
```

### Link biomass stability with community structure

```{r stab-div-mult, fig.dim = c(10, 7), fig.cap = "Link between the stability of biomass and diversity"}
biomass_com <- temporal_community_metrics %>%
  left_join(select(synchrony, station, synchrony, cv_sp)) %>%
  select(biomass_stab, synchrony, cv_sp, richness_cv, richness_med, betadiv) %>%
  gather(diversity, div_value, richness_med, richness_cv, betadiv) %>%
  gather(stability, stab_value, biomass_stab, synchrony, cv_sp)

formula <- y ~ x #needed for stat_poly_eq
qplot(div_value, stab_value, data =  biomass_com, geom = "point") +
  facet_grid(stability ~ diversity, labeller = mylabel(), scales = "free") +
  geom_smooth(method = 'lm') +
  stat_poly_eq(
    formula = formula,
    eq.with.lhs = "italic(hat(y))~`=`~",
    aes(label = paste(..eq.label.., ..rr.label.., sep = "*plain(\",\")~")),
    parse = TRUE) +
  labs(x = "Diversity", y = "Stability component")
```

```{r stab-net, fig.cap = "Link between biomass stability and network structure (median)"}
# plot
avg_network <- temporal_network_metrics %>%
  select_at(vars(dplyr::matches("med|station")))
biomass_stab_station <- temporal_community_metrics %>%
  select(station, biomass_stab)
stab_biomass_net_avg <- left_join(avg_network, biomass_stab_station) %>%
  gather(metrics, values, colnames(select_at(., vars((dplyr::matches("med")))))) %>%
  mutate(metrics = str_replace(metrics, "_med", "")) %>%
  filter(metrics != "nbnode")

# TODO: think about not facetting (list of plots ?)
# Facet label:
formula <- y ~ x #needed for stat_poly_eq
p <- ggplot(stab_biomass_net_avg, aes(y = biomass_stab, x = values)) +
  geom_point() +
  facet_wrap(~ metrics, labeller = mylabel(), scales = "free_x") +
  geom_smooth(method = 'lm') +
  stat_poly_eq(
    formula = formula,
    eq.with.lhs = "italic(hat(y))~`=`~",
    aes(label = paste(..eq.label.., ..rr.label.., sep = "*plain(\",\")~")),
    parse = TRUE) +
  labs(
    x = "Median of the network indices",
    y = "Biomass stability"
  )
p
```

```{r stab-comp, fig.cap = "Link between biomass stability by trophic group and total species richness (median)"}
myload(temporal_network_metrics, dir = mypath("data", "classes"))
net_troph_group <- temporal_network_metrics %>% 
  unnest(troph_group) %>%
  mutate(troph_group = as.factor(troph_group))
net_troph_group %<>%
  select_at(vars(dplyr::matches("_med|stab|station|troph_group"))) %>%
  gather(metrics, values, colnames(select_at(., vars((dplyr::matches("med")))))) %>%
  mutate(metrics = str_replace(metrics, "_med", ""))
p <- ggplot(net_troph_group, aes(y = biomass_stab, x = values, color = troph_group)) +
  geom_point() +
  ggplot2::scale_fill_manual(
    labels = troph_group_labeller(),
    values = c("blue", "green", "red"),
    name = "Trophic level"
    ) +
  facet_wrap(~metrics, labeller = mylabel(), scales = "free_x") +
  geom_smooth(method = 'lm')+
  stat_poly_eq(
    formula = formula,
    eq.with.lhs = "italic(hat(y))~`=`~",
    aes(label = paste(..eq.label.., ..rr.label.., sep = "*plain(\",\")~")),
    parse = TRUE) +
  xylabs(
    x = "network_med",
    y = "biomass_stab"
  )
p
```

The Figure \@ref(fig:stab-comp) showed that medium trophic level part of the
network had a positive stability-diversity relationship with while high
trophic level had a negative one.  
Furthermore, we see that high trophic level compartment had a highest stability
than the medium compartment. In the same vein, the latter pattern is confirmed when looking at the richness by compartment instead of the total richness (Figure \@ref(fig:stab-comp2)).

```{r stab-comp2, fig.dim = c(10, 7), fig.cap = "Link between biomass stability and species richness by trophic group (median)"}
net_troph_group <- temporal_network_metrics %>% 
  select(station, troph_group) %>%
  unnest() %>%
  filter(!is.na(troph_group)) %>%
  mutate(troph_group = as.factor(troph_group))
plot_stab_richness_troph_group <-
  ggplot(net_troph_group, aes(y = log(biomass_stab), x = richness_avg)) +
  geom_point() +
  facet_grid(cols = vars(troph_group)) +
  geom_smooth(method = 'lm')+
  stat_poly_eq(
    formula = formula,
    eq.with.lhs = "italic(hat(y))~`=`~",
    aes(label = paste(..eq.label.., ..rr.label.., sep = "*plain(\",\")~")),
    parse = TRUE) +
  xylabs(
    x = "richness_avg",
    y = "biomass_stab"
  )
plot_stab_richness_troph_group
```

One hypothesis to explain this opposite pattern might be a disequilibrium
between the two compartment. We can imagine that each compartment can
destabilize each other according to the part of the total biomass of total
species richness that there are in each of them. The figure
\@ref(fig:stab-comp-ratio) showed that the biomass stability of the medium
compartment decreased with the increase of biomass and species number ratio in
the high compartment and we observed the reverse for the high trophic
compartment.

We are looking forward to fully understand why we observed this inverse
relationship.

```{r stab-comp-ratio, fig.cap = "Biomass stability and ratio of biomass and species number (top and bottom panel resp.) in the high trophic level"}
ratio_sp <- net_troph_group %>%
  select(station, troph_group, richness_avg) %>%
  spread(troph_group, richness_avg) %>%
  mutate(sp_h_m = `3` / (`3` + `2`)) %>%
  select(station, sp_h_m)

ratio_bm <- net_troph_group %>%
  select(station, troph_group, biomass_avg) %>%
  spread(troph_group, biomass_avg) %>%
  mutate(bm_h_m = `3` / (`3` + `2`)) %>%
  select(station, bm_h_m)

net_troph_group <- temporal_network_metrics %>%
  left_join(ratio_sp, by = "station") %>%
  left_join(ratio_bm, by = "station") %>%
  select(station, troph_group, sp_h_m, bm_h_m) %>%
  unnest() %>%
  filter(!is.na(troph_group), troph_group != 1) %>%
  mutate(troph_group = as.factor(troph_group)) %>%
  gather(ratio_troph, value, sp_h_m, bm_h_m)

plot_stab_richness_troph_group <-
  ggplot(net_troph_group, aes(y = log(biomass_stab), x = value)) +
  geom_point() +
  facet_grid(cols = vars(troph_group), rows = vars(ratio_troph), labeller =
    troph_group_labeller()) +
  geom_smooth(method = 'lm')+
  stat_poly_eq(
    formula = formula,
    eq.with.lhs = "italic(hat(y))~`=`~",
    aes(label = paste(..eq.label.., ..rr.label.., sep = "*plain(\",\")~")),
    parse = TRUE) +
  xylabs(
    y = "biomass_stab"
  ) + 
    xlab("Ratio of biomass and species nb in high troph compartment compare to total")
plot_stab_richness_troph_group
```

## Pressure

## SEM

### All

### By basin

>>>>

```{r net-cor-med, fig.cap = "Correlation between network indices (median over the temporal series). "}
# Get network metrics
myload(temporal_network_metrics, dir = mypath("data", "classes"))
temporal_network_metrics_classes <- temporal_network_metrics
myload(temporal_network_metrics, dir = dest_dir)
myload(temporal_community_metrics, synchrony, dir = data_common)

@@

plot_grid(eig_plot, pca_plot[[1]], pca_plot[[2]], pca_plot[[3]], labels =
  "AUTO")
```

@@

### 2019-11-13 report/05-stability.Rmd
Update report

```{r}
myload(temporal_network_metrics, dir = mypath("data", "cl~/Documents/post-these/mnhn/fishcom/report/index.Rmdasses"))
temporal_network_metrics_classes <- temporal_network_metrics
myload(temporal_network_metrics, dir = dest_dir)
myload(temporal_community_metrics, synchrony, op_analysis, dir = data_common)
```

@@

@@

```{r}
myload(network_analysis, dir = mypath("data", "classes"))
test <- select(network_analysis, opcod, composition) %>%
  unnest(composition)
test2 <- get_sync_cv_mat(com_analysis = test, op_analysis = op_analysis)

# TODO: Plot for the five stations the most and the less stable:
plot_dyn_sp_biomass(sync = test2, station = 122, .log = TRUE)
plot_dyn_sp_biomass(sync = test2, station = 21877, .log = TRUE)
```

@@

plot_stab_richness_troph_group <-
  ggplot(net_troph_group, aes(y = log(biomass_stab), x = value)) +
  geom_point() +
  facet_grid(cols = vars(troph_group), rows = vars(ratio_troph), labeller =
    troph_group_labeller()) +
  geom_smooth(method = 'lm')+
  stat_poly_eq(
    formula = formula,
    eq.with.lhs = "italic(hat(y))~`=`~",
    aes(label = paste(..eq.label.., ..rr.label.., sep = "*plain(\",\")~")),
    parse = TRUE) +
  xylabs(
    y = "biomass_stab"
  ) + 
    xlab("Ratio of biomass and species nb in high troph compartment compare to total")
plot_stab_richness_troph_group
```

>>>>

```{r}
myload(temporal_network_metrics, dir = mypath("data", "classes"))
temporal_network_metrics_classes <- temporal_network_metrics
myload(temporal_network_metrics, dir = dest_dir)
myload(temporal_community_metrics, synchrony, op_analysis, dir = data_common)
```

@@

#### Total biomass

@@

```{r more-stab-troph, fig.dim = c(10, 21), fig.cap = "The four station with the highest biomass stability. Dashed and solid lines represent respectively trophic species in the group 2 and 3."}

myload(network_analysis, dir = mypath("data", "classes"))
myload(trophic_level, trophic_class, dir = mypath("data"))
source(mypath("R", "synchrony.R"))
source(mypath("R", "local_network_build.R"))
# Get biomass by sp node:
net_sp_troph <- select(network_analysis, opcod, composition) %>%
  unnest(composition)
# Get synchrony and cv sp:
sync_sp_troph <- get_sync_cv_mat(com_analysis = net_sp_troph, op_analysis = op_analysis) %>%
  arrange(cv_com)
# Get trophic lvl by node
trophic_level %<>%
  rename(species = sp_class) %>%
  mutate( troph_group = get_size_class(trophic_level, NULL, troph_level,
      trophic_class))

plot_stab <- purrr::map(station_high_low_stab, function (x) {
  p <- plot_dyn_sp_biomass(sync = sync_sp_troph, trophic_level = trophic_level, station = x, .log = TRUE)
  p + theme(legend.position="none") 
})
plot_grid(plotlist = plot_stab, ncol = 2)
```

```{r less-stab-troph, fig.dim = c(10, 7), fig.cap = "The four station with the lowest biomass stability. See caption of Figure for details."}
plot_grid(plotlist = plot_stab[7:8], ncol = 2)
```

```{r mid-stab-troph, fig.dim = c(10, 7), fig.cap = "Four stations with medium biomass stability. See caption of Figure for details."}
# Middle station 
plot_stab <- purrr::map(sync_sp_troph$station[209:212], function (x) {
  p <- plot_dyn_sp_biomass(sync = sync_sp_troph, trophic_level = trophic_level, station = x, .log = TRUE)
  p + theme(legend.position="none") 
})
plot_grid(plotlist = plot_stab[1:4], ncol = 2)
```

```{r 75-stab-troph, fig.dim = c(10, 7), fig.cap = "Four stations with medium/low biomass stability. See caption of Figure for details."}
# Third quater
plot_stab <- purrr::map(sync_sp_troph$station[300:304], function (x) {
  p <- plot_dyn_sp_biomass(sync = sync_sp_troph, trophic_level = trophic_level, station = x, .log = FALSE)
  p + theme(legend.position="none") 
})
plot_grid(plotlist = plot_stab[1:4], ncol = 2)
```

```{r 25-stab-troph, fig.dim = c(10, 7), fig.cap = "Four stations with medium/low biomass stability. See caption of Figure for details."}
# Third quater
plot_stab <- purrr::map(sync_sp_troph$station[104:107], function (x) {
  p <- plot_dyn_sp_biomass(sync = sync_sp_troph, trophic_level = trophic_level, station = x, .log = FALSE)
  p + theme(legend.position="none") 
})
plot_grid(plotlist = plot_stab[1:10], ncol = 2)
```

### CV sp

```{r abun-sp, fig.cap = "Species most abundant by trophic group."}
# Sp the most abundant by group
bm_sp_troph_grp <- net_sp_troph %>%
  filter(!is.na(troph_group) & troph_group != 1) %>%
  group_by(troph_group, sp_class) %>%
  summarise(biomass = mean(biomass)) %>%
  arrange(desc(biomass)) %>%
  slice(1:20)

p_bm <- map(c(2, 3), .f = function(x) {
  mylim <- sapply(c(min, max),
    FUN = function(x) x(bm_sp_troph_grp$biomass))

  .data <- bm_sp_troph_grp %>%
    filter(troph_group == x)
  if (x == 2) {
    tmp_title <- paste("Medium trophic group (2)")
  } else {
    tmp_title <- paste("High trophic group (3)")
  }

  ggplot(data = .data, aes(x = sp_class, y = biomass)) +
    geom_point() +
    labs(x = "Trophic species", y = "Biomass (g)", title = tmp_title) +
    ylim(mylim[1], mylim[2])

})
plot_grid(plotlist = p_bm, ncol = 2)
```

```{r}
# I need:
# - by species:
#   - CV
#   - Biomass 
# - by Trophic group:
#   - Species richness 
#   - CV
#   - biomass

# Species

## Variance by sp and station:
var_sp <- sync_sp_troph %>%
  select(station, var_sp) %>%
  mutate(var_sp = map(var_sp, ~enframe(.x))) %>%
  unnest(var_sp) %>%
  rename(species = name, var_sp = value)
## Average biomass by sp and station:
avg_sp <- sync_sp_troph %>%
  select(station, avg_sp) %>%
  mutate(avg_sp = map(avg_sp, ~enframe(.x))) %>%
  unnest(avg_sp) %>%
  rename(species = name, avg_sp = value)
## CV and biomass by sp and station  
cv_bm_sp <- left_join(avg_sp, var_sp, by = c("station", "species")) %>%
  mutate(cv = sqrt(var_sp) / avg_sp, var_sp = NULL) %>%
  rename(bm = avg_sp)

# By trophic group:

## CV, biomass and div (ALREADY DONE!)
cv_bm_div_troph_grp <- temporal_network_metrics_classes %>% 
  select(station, troph_group) %>%
  unnest(troph_group) %>%
  filter(!is.na(troph_group) & troph_group != 1) %>%
  rename(bm_st = biomass_avg, div_st = richness_avg, cv_st = biomass_cv) %>%
  mutate(troph_group = as.factor(troph_group))
```

#### CV sp VS CV group

```{r}
cv_sp_grp <- left_join(select(cv_bm_sp, -bm),
  select(cv_bm_div_troph_grp, -biomass_stab), by = "station")

ang9 <- cv_sp_grp %>%
  filter(species == "ANG_9")

```

@@

plot_stab_richness_troph_group <-
  ggplot(net_troph_group, aes(y = log(biomass_stab), x = value)) +
  geom_point(aes(color = richness_avg)) +
  facet_grid(cols = vars(troph_group), rows = vars(ratio_troph), labeller =
    troph_group_labeller()) +
  geom_smooth(method = 'lm')+
  stat_poly_eq(
    formula = formula,
    eq.with.lhs = "italic(hat(y))~`=`~",
    aes(label = paste(..eq.label.., ..rr.label.., sep = "*plain(\",\")~")),
    parse = TRUE) +
  xylabs(
    y = "biomass_stab"
  ) + 
    xlab("Ratio of biomass and species nb in high troph compartment compare to total")
plot_stab_richness_troph_group

```
